---
title: "Shiny Simple Tutorial"
author: "Girija Attigeri"
date: "July 22, 2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

- Simple Example of Creation of Shiny App. 
- The application is designed to add or multiply two numbers. 

## Feartures 

  - Add numbers in the textboxes provided. minimum number to be entered is zero, maximum is 100
  - Select the proper radio button either add or multiply
```{r eval=FALSE,echo=TRUE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("Add or multiply numbers"),
  sidebarLayout(
    sidebarPanel(
      numericInput("numeric1", "First Number ", 
                   value = 1000, min = 1, max = 1000, step = 1),
      numericInput("numeric2", "Second Number", 
                   value = 1000, min = 1, max = 1000, step = 1),
      radioButtons("radio", label = h3("Radio buttons"),
                   choices = list("Add" = 1, "Multiply" = 2),
                   selected = 1)
    ),
    mainPanel( h3("Output"),textOutput("sum")
    )  ) ))
```

## Slide with R Output

```{r ,echo=FALSE}
library(png)
library(grid)
img <- readPNG("D://RStudio//ddp.png")
 grid.raster(img)
```
!["Figure"] D:\\RStudio\\ddp.png
```

## Conclusion
-Based on th radio button input two numbers were added or multiplied

Thank you

